\myTitle

### 2024-07-15 author-title-etc.tex
MGD added TJS's changes
added draft abstract
Tiny tweaks before submitting

% redefine this to make author list. Note affiliation symbols are done manually.
% All caps tends to look better
\newcommand{\myAuthors}{Eric C. Anderson$^{*,\dagger,\ddag,\S}$, Rachel M. Giglio$^{\#}$, Matthew G. DeSaix$^{\ddag,\#}$ Timothy J. Smyser$^{\#}$}
\author{Eric C. Anderson$^{*,\dagger,\ddag,\S}$, Rachel M. Giglio$^{\#}$, Matthew G. DeSaix$^{\ddag,\#}$ Timothy J. Smyser$^{\#}$}

@@

\renewcommand{\KeyWords}{genetic stock identification, mixture deconvolution, permutation testing, power analysis, blah, blah}

@@

% here you can put your very own copyright notice
\newcommand{\myCopyright}{\copyright US Federal Government work in the public domain in the USA}

>>>>

% redefine this to make author list. Note affiliation symbols are done manually.
% All caps tends to look better
\newcommand{\myAuthors}{Eric C. Anderson$^{*,\dagger,\ddag,\S}$, Rachael M. Giglio$^{\#}$, Matthew G. DeSaix$^{\ddag,\#}$ Timothy J. Smyser$^{\#}$}
\author{Eric C. Anderson$^{*,\dagger,\ddag,\S}$, Rachael M. Giglio$^{\#}$, Matthew G. DeSaix$^{\ddag,\#}$ Timothy J. Smyser$^{\#}$}

@@

\renewcommand{\KeyWords}{genetic stock identification, mixture deconvolution, permutation testing, power analysis, R package}

@@

% here you can put your very own copyright notice
\newcommand{\myCopyright}{}
